Legion: Expressing Locality and Independence with Logical Regions

### 2012-08-09 doc/sc2012/legion.tex
Fixing some contract stuff for darpa

\title{Legion: Expressing Locality and Independence with Logical
  Regions\thanks{This work was supported by the Army High Performance
    Research Center (DARPA contract HR0011-10-9-0008), a subcontract
    from Los Alamos National Laboratory for the DOE Office of Science,
    Advanced Scientific Computing Research (DE-AC52-06NA25396), and NVIDIA.  The views and
    conclusions contained in this document are those of the authors
    and should not be interpreted as representing the official
    policies, either expressed or implied, of the U.S. Government.}}
%\author{ \IEEEauthorblockN{Michael Bauer\IEEEauthorrefmark{1},
%%\authorinfo(Stanford University, email: \mbox{mebauer@cs.stanford.edu}
%Sean Treichler\IEEEauthorrefmark{1}, 
%%\authorinfo(Stanford University, email: \mbox{sjt@cs.stanford.edu}
%Elliott Slaughter\IEEEauthorrefmark{1}, 
%% \authorinfo(Stanford University, email: \mbox{slaughter@cs.stanford.edu}
%Alex Aiken\IEEEauthorrefmark{1}  
%%\authorinfo(Stanford University, email: \mbox{aiken@cs.stanford.edu}
%%\email{aiken@cs.stanford.edu}
%}
%\IEEEauthorblockA{
%\IEEEauthorrefmark{1}{Computer Science Department, Stanford University}
%}
%}

>>>>

\title{Legion: Expressing Locality and Independence with Logical
  Regions\thanks{This work was supported by the DARPA UHPC project
    through a subcontract of NVIDIA (DARPA contract HR0011-10-9-0008),
    and by the Army High Performance Research Center, through a subcontract
    from Los Alamos National Laboratory for the DOE Office of Science,
    Advanced Scientific Computing Research (DE-AC52-06NA25396).  The views and
    conclusions contained in this document are those of the authors
    and should not be interpreted as representing the official
    policies, either expressed or implied, of the U.S. Government.}}
%\author{ \IEEEauthorblockN{Michael Bauer\IEEEauthorrefmark{1},
%%\authorinfo(Stanford University, email: \mbox{mebauer@cs.stanford.edu}
%Sean Treichler\IEEEauthorrefmark{1}, 
%%\authorinfo(Stanford University, email: \mbox{sjt@cs.stanford.edu}
%Elliott Slaughter\IEEEauthorrefmark{1}, 
%% \authorinfo(Stanford University, email: \mbox{slaughter@cs.stanford.edu}
%Alex Aiken\IEEEauthorrefmark{1}  
%%\authorinfo(Stanford University, email: \mbox{aiken@cs.stanford.edu}
%%\email{aiken@cs.stanford.edu}
%}
%\IEEEauthorblockA{
%\IEEEauthorrefmark{1}{Computer Science Department, Stanford University}
%}
%}
